PrepCAISOData

### 2014-12-23 CAData/CAISO/LoadData.Rmd
Data in and model made but counterfactuals work too.

>>>>

```{r}
Trends<- read.csv("~/Forecast-Peak-With-Google-Trends/CAData/TrendsCAWeeklyEdited.csv")

#Extract the end of week.
library(stringr)
Trends$EndDate<-as.Date(str_sub(Trends$Week,14))
summary(Trends)

Now lets hook this to the load and forecast data.

```{r}
library(sqldf)
Trends$LastDate<-Trends$EndDate+7

WTrends<-sqldf("select Current.*, Trends.* from Current, Trends where Current.Date>Trends.EndDate and Current.Date<=Trends.LastDate;   ")

summary(WTrends)
```

On to the modeling

```{r}
Base<-lm(Actual~Forecast,data=WTrends)
summary(Base)

WWeather<-lm(Actual~Forecast+weather,data=WTrends)
summary(WWeather)

anova(Base,WWeather)
```

Concept proved.

Try counterfactuals

```{r}
summary(lm(Actual~Forecast+traffic,data=WTrends))

summary(lm(Actual~Forecast+restaurants,data=WTrends))

summary(lm(Actual~Forecast+gas,data=WTrends))

summary(lm(Actual~Forecast+movies,data=WTrends))
```
Well that sucks.  All the counterfactuals work too.  Check F test

anova(Base,lm(Actual~Forecast+traffic,data=WTrends))

anova(Base,lm(Actual~Forecast+restaurants,data=WTrends))

anova(Base,lm(Actual~Forecast+gas,data=WTrends))

anova(Base,lm(Actual~Forecast+movies,data=WTrends))
```
Now that is an interesting puzzel.
